Paper_analyses

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
quick visualisation
quick vis of arousal sample and iaps correlation for positive negative and neutral. this shows we do have enough variance and at all levels we see a correlation between arousal

>>>>

# Plot just positive
tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ground_valence_2 == "positive")%>%
  group_by(stimDescription,ground_valence_2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(stimDescription, arousal))+
  # geom_point()+
  stat_summary(funy = mean, geom = 'pointrange', color = "blue")+
   stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange', color = "red")+
  theme(axis.text.x = element_text(angle = 60))

# negative
tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ground_valence_2 == "negative")%>%
  group_by(stimDescription,ground_valence_2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(stimDescription, arousal))+
  # geom_point()+
  stat_summary(funy = mean, geom = 'pointrange', color = "blue")+
   stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange', color = "red")+
  theme(axis.text.x = element_text(angle = 60))

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ground_valence_2 == "positive")%>%
  group_by(stimIAPS,ground_valence_2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ArousalMean, arousal))+
  geom_point()+
  geom_smooth(method = 'lm')+
  ggpubr::stat_cor()

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ground_valence_2 == "negative")%>%
  group_by(stimIAPS,ground_valence_2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ArousalMean, arousal))+
  geom_point()+
  geom_smooth(method = 'lm')+
  ggpubr::stat_cor()

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ground_valence_2 == "neutral")%>%
  group_by(stimIAPS,ground_valence_2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ArousalMean, arousal))+
  geom_point()+
  geom_smooth(method = 'lm')+
  ggpubr::stat_cor()

  # geom_point()+
  stat_summary(funy = mean, geom = 'pointrange', color = "blue")+
   stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange', color = "red")+
  theme(axis.text.x = element_text(angle = 60))
